Analysis of Text Reuse in the Field Code

### 2015-12-03 index.Rmd
Infrastructure for web notebook

---
title: "Field Code Analysis"
author: "Lincoln Mullen and Kellen Funk"
output: html_document
---

>>>>

---
title: "Analysis of Text Reuse in the Field Code"
author: "Lincoln Mullen and Kellen Funk"
---

This is an analysis notebook for detecting text reuse in codes of civil procedure---the "Field codes"---in the nineteenth-century United States. It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com).

See these links for more details:

- [Kellen's posts about the project](http://kellenfunk.org/field-code/)
- [An Introduction to the textreuse Package, with Suggested Applications](http://lincolnmullen.com/blog/an-introduction-to-the-textreuse-package/)
- [Detecting Text Reuse in Nineteenth-Century Legal Documents](http://lincolnmullen.com/blog/detecting-text-reuse-in-legal-documents/)

This notebook contains our work in progress. This is the most recent analysis in progress. There is more in the [repository](https://github.com/lmullen/civil-procedure-codes).
